%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% Based on:
% https://github.com/deedydas/Deedy-Resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume}
\usepackage{fontawesome5}

\begin{document}
\vspace{+30ex}

\raggedright
\namesection{}{}{ {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Breno LEVI} \\ \\
5G and Cellular System Engineer with Global Telecom Expertise in Product Development, \\
Network Optimization, Performance Testing, and 3GPP Standards Compliance}
\vspace{+3ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%a
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}


\begin{center}
\vspace{+3ex}
\end{center}

{\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries \Large{Breno LEVI}} \\
\textit{ }\\
\faHome \ Paris, France\\
 ~ \faPhone \ +33~xx~xx~xx~xx~xx\\
 ~ \faGithub \ \href{https://github.com/blevic}{github.com/blevic} \\
 ~ \faLinkedin \ \href{https://www.linkedin.com/in/brenolevi/}{linkedin.com/in/brenolevi} \\
 ~ \faEnvelope \ \href{mailto:xxxxxxxxxx@gmail.com}{xxxxxxxxxx@gmail.com}   
\sectionsep

\vspace{+3ex}

\section{Languages} 
\begin{tabular}{ll}
\custombold{Portuguese}         & Native\\
\custombold{English:}             & Fluent \\
\rule{4pt}{0ex} \textbullet{}TOEFL iBT & 113/120 -- C1\\
\custombold{French:}              & Fluent \\
\rule{4pt}{0ex} \textbullet{}TFI & 930/990 -- C1\\
\custombold{Spanish}             & Advanced
\end{tabular}
\sectionsep

\vspace{+1ex}

\section{Software}

\subsection{Languages}
Python, C, C++, Java, JavaScript, 
SQL, Assembly, VHDL, Shell 
\sectionsep

\subsection{Programs}
Wireshark, QXDM, QCAT, ELT, MATLAB, 
Mathematica, SolidWorks, Android Studio,
PostgreSQL, Simulink, Amesim, Xcode
\sectionsep

\subsection{Other}
Git, Gerrit, Jira, Office, LaTeX, AOSP

\vspace{+2ex}
\section{Distinctions} 
\begin{tabular}{rll}
2021         & Partner Award (Motorola)\\
2019         & Motorola Hackathon (3rd Best)\\
2017	     & Eiffel Excellence Scholarship\\
2014         & PICME Scholarship (CNPq)\\
2012	     & 6th IOAA -- Bronze\\
%2012	     & OBMEP -- Gold\\
%2012	     & OBA -- Gold \\
%2012        & PIC scholarship (CNPq)\\
%2011	     & OBMEP -- Gold \\
%2011	     & OBA -- Gold \\
%2011	     & OBF -- Bronze
\end{tabular}
\sectionsep

\section{Patent}
\href{https://patents.google.com/patent/US11308923B2/}{US 11,308,923 B2} - ``Electronic device with face orienting user interface''. Motorola Mobility LLC, assignee. Issued 2022.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\section{Experiences}

\runsubsection{ALTEN / SAGEMCOM}
\descript{| 5G System Engineer}
\location{Jun. 2023 -- Present | Paris, France}
\rule{8pt}{0ex} \textbullet{Technical reference for all mobile network topics, supporting FWA product development across SW, HW, validation, core platform, and project teams.} \\
\rule{8pt}{0ex} \textbullet{Collaborate with major telecom operators, chipset vendors, and certification labs to ensure compliance, integration, and network optimization.}\\
\rule{8pt}{0ex} \textbullet{Lead the development of 5G product validation, implementing automated tools for capability assessment, performance analysis, and throughput testing.}\\
\rule{8pt}{0ex} \textbullet{Configure and manage 5G cell simulators, including Amarisoft, Keysight, Anritsu and R\&S callboxes for testing and validation.}\\
\rule{8pt}{0ex} \textbullet{Conduct internal 5G training sessions for cross-functional teams, enhancing company-wide expertise in mobile network technologies.}
\sectionsep

\runsubsection{Motorola}
\descript{| Staff Engineer}
\location{May 2022 -- May 2023 | São Paulo, Brazil}
\rule{8pt}{0ex} \textbullet{Responsible for product's network, modem, and baseband configuration, working within a global team serving multiple telecom carriers as clients.} \\
\rule{8pt}{0ex} \textbullet{Led the development of advanced performance analysis tools for cellular technologies, including 5G NR, LTE, UMTS, GSM, IMS, and VoLTE/VoWiFi.} \\
\rule{8pt}{0ex} \textbullet{Developed automation solutions for embedded Android and AOSP, integrating Python-based tools with CI/CD pipelines.}
\sectionsep

\runsubsection{Motorola / IPE}
\descript{| Software Analyst}
\location{Jun. 2019 -- May 2022 | Campinas, Brazil}
\rule{8pt}{0ex} \textbullet{Led the bring-up and integration of a low-level software interface to collect valuable 5G KPIs from large-scale deployments.} \\
\rule{8pt}{0ex} \textbullet{Analyzed and troubleshot network and UE issues across multiple cellular technologies (5G NR, LTE, IMS, UMTS, GSM, CDMA).}\\
\rule{8pt}{0ex} \textbullet{Worked with baseband logs (Qualcomm/MTK) and wireless test platforms (Keysight UXM, R\&S CMW500) for debugging and protocol validation.}\\

\sectionsep

\runsubsection{Motorola}
\descript{| R\&D Intern}
\location{Jul. 2018 -- Jun. 2019 | Jaguariúna, Brazil}
\rule{8pt}{0ex} \textbullet{Developed and maintained tools for analyzing device performance in cellular networks using Qualcomm debugging tools (QCAT, QXDM).}
\sectionsep

\runsubsection{Sterblue}
\descript{| Engineering Intern}
\location{Apr. 2017 -- Aug. 2017 | Nantes, France}
\rule{8pt}{0ex}\textbullet{Designed and implemented an automated, connected drone station, overseeing control processes, component sourcing, and system automation.}
\sectionsep

%\runsubsection{Centrale Nantes}
%\descript{| Academic project}
%\location{Nov. 2016 -- Mar. 2017 | Nantes, France}
%\rule{8pt}{0ex}Project ``Study of a motorized inverted pendulum'' \\
%\rule{8pt}{0ex}\textbullet{ Application of command techniques to control a dicycle with an Arduino}
%\sectionsep

%\runsubsection{LAMAP44}
%\descript{| Industrial study project}
%\location{Nov. 2015 -- Apr. 2016 | Nantes, France}
%\rule{8pt}{0ex}Development of an eductional kit about renewable marine energies\\
%\rule{8pt}{0ex}\textbullet{ Project management, writing documents for clients, team work}
%\sectionsep

%\runsubsection{UNICAMP -- Inst. of Mathematics}
%\descript{| Research project}
%\location{Apr. 2013 -- Jun.2015 | Campinas, Brazil}
%\rule{8pt}{0ex}Project ``Introduction to topology''\\
%\rule{8pt}{0ex}\textbullet{ Demonstration of Tychonoff's and Seifert-van Kampen's theorem}\\
%\rule{8pt}{0ex}\textbullet{ Presentation of the results during two seminars at IMECC (UNICAMP)}
%\sectionsep

%\runsubsection{UFV - Dep. of Mathematics}
%\descript{| Study group}
%\location{Jul. 2012 -- Jun. 2013 | Viçosa, Brazil}
%\rule{8pt}{0ex}Advanced studies in mathematics for high performance students
%\sectionsep

%\runsubsection{UFV - Dep. of Mechanical Eng.}
%\descript{| Scientific Initiation}
%\location{Jul. 2011 -- Jun. 2012 | Viçosa, Brazil}
%\rule{8pt}{0ex} Study of metalurgy in the MIG, TIG and shielded metal welding processes\\
%\rule{8pt}{0ex}\textbullet{ Laboratory manipulations, bibliographic research}
%\sectionsep


\section{Education}

\runsubsection{École Centrale de Nantes}
\descript{| Master's Degree}
\location{Sep. 2015 – Aug. 2017 | Nantes, France}
\vspace{\topsep}
\begin{tightemize}\item Master's degree in a double graduation program: generalist engineering
\item Excellence scholarship offered by French Ministry of Foreign Affairs
%\item ``Embedded systems and power grids'' as curricular option
\end{tightemize}
\sectionsep

\runsubsection{University of Campinas}
\descript{| Bachelor's Degree}
\location{Mar. 2013 – Aug. 2019 | Campinas, Brazil}
\begin{tightemize}\item Bachelor's degree in Electrical Engineering; 1st decile performance
\item Energy, electronics, computing, control, automation and telecommunication
%\item Specialization study certificate in control systems
\end{tightemize}
\sectionsep

%\runsubsection{University of Beihang}
%\descript{| Summer course}
%\location{Jul. 2016 | Beijing, China}
%\begin{tightemize}\item Corporate finance and International business law
%\end{tightemize}

\end{minipage} 


\end{document}  \documentclass[]{article}
